A Neural Network Alternative to Convolutive Audio Models for Source Separation

### 2017-06-12 paper/paper.tex
Added the CNN-CNN block diagram

      \node [,name=input] (input) {$X$};
      \coordinate [, name=rinput, right of=input, node distance=2cm ](rinput) {};

      \node [, right of=rinput] (controller) {$\vdots$};
      \node [block, above of=controller,node distance=1.3cm] (up){$\mathbf W^\ddagger_1$};
      \node [block, below of=controller,node distance=1.3cm] (rate) {$\mathbf W^\ddagger_K$};
      \node [sum, right of=controller,node distance=2cm] (sum2) {CT};

      \node [block, right of=sum2,node distance=2cm] (system) {$\frac{a_{\beta 2}}{s+a_{\beta 1}}$};
      \node [output, right of=system, node distance=2cm] (output) {};
      \node [tmp, below of=controller] (tmp1){$H(s)$};

      \draw [->] (rinput) -- (controller); 
      \draw [->] (controller) -- (sum2);
      \draw [->] (sum2) -- node{$U(s)$} (system);
     % \draw [->] (system) -- node [name=y] {$Y(s)$}(output);
      \draw [->] (rinput) |- (rate);
      \draw [->] (rate) -| (sum2);
      \draw [->] (rinput) |- (up);
      \draw [->] (up) -| (sum2);
      % \draw [->] (y) |- (tmp1)-| node[pos=0.99] {$-$} (sum1);
      %\draw [->] (extra)--(sum2);
      %\draw [->] ($(0,1.5cm)+(extra)$)node[above]{$d_{\beta 2}$} -- (extra);
    \end{tikzpicture}
  \caption{Block Diagram of CNN-CNN Autoencoder} 
  \label{CNN-CNN Auto Encoder}
\end{figure*}

>>>>

      \node [,name=input] (input) {$\mathbf X$};
      \coordinate [, name=rinput, right of=input, node distance=1.3cm ](rinput) {};
      \node [block, right of=rinput, node distance=1.3cm] (controller) {$\vdots$};
      \node [sum, right of=controller, node distance=2cm] (controllers){$\sum_j$};
      \node [block, above of=controller,node distance=1.3cm] (up){$\mathbf X *\mathbf W^\ddagger_1$};
      \node [sum, right of=up, node distance=2cm] (ups) {$\sum_j$};
      \node [block, below of=controller,node distance=1.3cm] (rate) {$\mathbf X*\mathbf W^\ddagger_K$};
      \node [sum, right of=rate, node distance=2cm] (rates) {$\sum_j$};

      \node [sum, right of=controllers,node distance=1.3cm] (sum2) {CT};
      \node[sum, right of=sum2,node distance=2cm] (system) {$g()$};
      \node [block, right of=system, node distance=2cm] (dec2) {$\vdots$};
      \node [block, above of=dec2, node distance=1.3cm] (dec1) {$\mathbf H(1, :) * \mathbf W_1$};
      \node [block, below of=dec2, node distance=1.3cm] (dec3) {$\mathbf H(K, :) *\mathbf W_K$};
      \node [sum, right of=dec2, node distance=2cm] (sum3) {$+$};
      \node [sum, right of=sum3, node distance=1.3cm] (g2) {$g()$};
      \node [,right of=g2, node distance=1.3cm] (outp) {$\widehat{\mathbf X}$};

      \draw [-] (input) -- (rinput);
      \draw [->] (rinput) -- (controller); 
      \draw [->] (controller) -- (controllers);
      \draw [->] (controllers) -- (sum2);
      \draw [->] (sum2) -- (system);
      \draw [->] (rinput) |- (rate);
      \draw [->] (rate) -- (rates);
      \draw [->] (rates) -| (sum2);
      \draw [->] (rinput) |- (up);
      \draw [->] (up) -- (ups);
      \draw [->] (ups) -| (sum2);
      \draw [->] (system) -- node {$\mathbf H(.,:)$} (dec2);
      \draw [->] (system) |- node {$\mathbf H(1,:)$} (dec1);
      \draw [->] (system) |- node[anchor=north]{$\mathbf H(K,:)$} (dec3);
      \draw [->] (dec1) -| (sum3);
      \draw [->] (dec2) -- (sum3);
      \draw [->] (dec3) -| (sum3);
      \draw [->] (sum3) -- (g2);
      \draw [->] (g2) -- (outp);
    \end{tikzpicture}
  \caption{Block Diagram of CNN-CNN Autoencoder} 
  \label{CNN-CNN Auto Encoder}
\end{figure*}
